A Constraint Solving Approach to Parikh Images of Regular Languages

### 2022-07-07 main.tex

The most obvious threats to validity would be poor benchmarking or poor
implementation, e.g. if the method described in \cref{sec:calculus,sec:multiple}
deviate from what is actually benchmarked in section \cref{sec:experiments}, or
if the methods used for benchmarking would be unsound. The first problem cannot
easily be addressed, except by stating that we have been careful in our
implementation and descriptions alike. The second is more practical. To increase
the probability that our results are indeed representative both in the sense of
representing runs on expected, real world input and in the statistical sense for
a given run of \Catra, despite the fact that we use randomness in our
implementation, we execute many experiments. During the development of \Catra{},
we have also executed experimeints on different hardware and software
configurations on smaller samples of instances to ensure that the general trend
holds. The logs from these executions are distributed along with notes as part
of the artefact in the interest of transparency. Moreover, we have validated
\Fudge{all reported satisfiable instances and their witnesses} with \Nuxmv{} to
ensure that \Calculus{} is indeed sound and does not cheat.

Another threat to validity would be if our implementations of the competition
(baseline and \Nuxmv) would deviate significantly from the expected
implementations. For \Nuxmv{} we use the default configuration which we believe
should be performant (or it should not be the default). Additionally, tweaking our invocation of \Nuxmv{} is explicitly made easy for artefact reviewers.

The most important and most probable threat to validity is our choice of
implementation platform and our choice of automata library, that is our choice
not to use one. Since our automata are more advanced than anything supported by
e.g. the BRICS library, we opted to use our own implementation. There are some
signs that in particular our product computation is inefficient, notably the
good performance of low-threshold automata materialisation that prioritises
computing smaller products. This means that our implementation of \Calculus{}
makes much less heavy use of our product construction library than the baseline
implementation does, instead putting its weight into \Princess{}' theorem
proving abilities. This situation would unfairly advantage \Calculus{} if our
automata library was indeed the bottleneck. We believe this is unlikely since
similar performance issues as the ones in baseline in our string solver was the
instigating reason for this research. Additionally, while we may have a
constant-factor performance impact from bad implementation, it is less likely
for our potentially poor implementation to be asymptotically worse than e.g.
BRICS. However, the performance improvement of \Calculus{} over baseline seen in
\cref{sec:experiments} is generally not constant.

>>>>

The most obvious threats to validity would be poor benchmarking or poor
implementation, e.g. if the method described in \cref{sec:calculus,sec:multiple}
deviate from what is actually benchmarked in section \cref{sec:experiments}, or
if the methods used for benchmarking would be unsound. The first problem cannot
easily be addressed, except by stating that we have been careful in our
implementation and descriptions alike. The second is more practical. To increase
the probability that our results are representative both in the sense of
representing runs on expected, real world input and in the statistical sense for
a given run of \Catra{} despite the use of randomness in our
implementation we execute many experiments. Moreover, we have validated all
reported solutions made by \Calculus{} with \Nuxmv{} to ensure that \Calculus{}
is indeed sound and does not cheat.

Another threat to validity would be if the competition (baseline and \Nuxmv)
would be disadvantaged in our comparison. For \Nuxmv{} we use the default
configuration which we believe should be performant (or it should not be the
default). Additionally, tweaking our invocation of \Nuxmv{} is explicitly made
easy for artefact reviewers. For baseline, our best argument is that the
solution we use is close to the one found in the \Ostrich{} string solver and
that it therefore should be realistic.

The most probable threat to validity is our choice of implementation platform
and our choice of automata library, that is our choice not to use one. Since our
automata are more advanced than anything supported by e.g. the BRICS library, we
opted to use our own implementation. There are some signs that in particular our
product computation is inefficient, notably the good performance of
low-threshold automata materialisation that prioritises computing smaller
products. This means that our implementation of \Calculus{} makes much less
heavy use of our product construction library than the baseline implementation
does, instead putting its weight into \Princess{}' theorem proving abilities.
This situation would unfairly advantage \Calculus{} if our automata library was
indeed the bottleneck. We believe this is unlikely since similar performance
issues as the ones in baseline in our string solver was the instigating reason
for this research. Additionally, while we may have a constant-factor performance
impact from bad implementation, it is less likely for our potentially poor
implementation to be asymptotically worse than e.g. BRICS. However, the
performance improvement of \Calculus{} over baseline seen in
\cref{sec:experiments} is generally not constant. Additionally, non-systematic
profiling suggests that both \Princess{}-based backends spend most of their time
in \Princess{}, suggesting that the automaton implementation is not the
bottleneck.
